Z-Resonance at LEP

### 2010-10-11 Z0-Publikation/tex/paper-template.tex
zweite aenderungen

\section{ Experiment}

LEP was designed to be able to deliver center of mass energies $\sqrt{s}$ from
some 89 up to \SI{209}{\giga\electronvolt}. This is enough to produce Z-bosons,
which should have a mass of about \SI{91}{\giga\electronvolt}, as it was
predicted by the standard model. Therefore the Z$^0$-particle was supposed to be
produced at LEP.

It can decay in various ways, but always into pairs of one
fermion and one antifermion. One of these possibilities is the decay via two
different quarks (Z$^0→qq'$), another one could be the decay via two
charged leptons like Z$^0→ μ^+μ^-$. The first one of the mentioned decays can be
seen as two jets which can be measured in hadronic calorimeters. The leptonic
decay is measured due to registration of leptons in electromagnetic
calorimeters, muon chambers or even hadronic calorimeters. All of the mentioned
detector layers have an almost cylindrical shape in order to
cover as much of the solid angle as possible. This is also the reason for the
installation of the end caps.

The detector for all of the possible standard model particles is LEP. Its
structure can be seen in \fref{aufbau}.
\begin{figure}[htb]
 \centering
 \includegraphics[page=5,viewport=286 620 508 765,clip,%
  width=\columnwidth,keepaspectratio]{../../Z0/docs/Z0ResFprakt}
 \caption{Design of the L3 detector.}% \cite{pic}.}
%  \todo[inline]{soll hier eine quelle hin?}
 \label{fig:aufbau}
\end{figure}
There are layers of components with different purposes. Starting from the
interaction point, these are the tracking chamber, the electromagnetic
calorimeter, the hadronic calorimeter and finally the muon chamber.

In this case the hadronic calorimeter and the muon chamber are the most
important parts. The hadronic calorimeter consists of alternating layers of
uranium plates and wire chambers. The muon chamber is built up of drift
chambers. It detects the high energy muons, which have passed the detector
without a significant loss of energy, because these are the only particles that
are able to reach there.
% Further information about the detector design can be found in \cite{script}.

>>>>

\section{ Experimental setup}

LEP was designed to be able to deliver center of mass energies $\sqrt{s}$ from
some 89 up to \SI{209}{\giga\electronvolt}. This is enough to produce Z-bosons,
which has a mass of about \SI{91}{\giga\electronvolt}, as it was
known from former measurements at SPPS. Therefore the Z$^0$-particle was
supposed to be produced at LEP.

It can decay in various ways, but always into pairs of one
fermion and one antifermion. One of these possibilities is the decay via two
different quarks (Z$^0→qq'$), another one could be the decay via two
charged leptons like Z$^0→ μ^+μ^-$. The first one of the mentioned decays can be
seen as two jets which can be measured in hadronic calorimeters. The leptonic
decay is measured due to registration of leptons in electromagnetic
calorimeters and muon chambers. All of the mentioned
detector layers have an almost cylindrical shape in order to
cover as much of the solid angle as possible. This is also the reason for the
installation of the end caps.

The particle detector LEP is built in a way as can be seen in \fref{aufbau}.
\begin{figure}[htb]
 \centering
 \includegraphics[page=5,viewport=286 620 508 765,clip,%
  width=\columnwidth,keepaspectratio]{../../Z0/docs/Z0ResFprakt}
 \caption{Design of the L3 detector.}% \cite{pic}.}
%  \todo[inline]{soll hier eine quelle hin?}
 \label{fig:aufbau}
\end{figure}
There are layers of components with different purposes. Starting from the
interaction point, these are the tracking chamber, the electromagnetic
calorimeter, the hadronic calorimeter and finally the muon chamber.

In this case the hadronic calorimeter and the muon chamber are the most
important parts, because in this study we focuss on muonic and hadronic
Z$^0$-decays. The hadronic calorimeter consists of alternating layers of
uranium plates and wire chambers. The muon chamber is built up of drift
chambers. It detects the high energy muons, which have passed the detector
without a significant loss of energy, because these are the only particles that
are able to reach there.
% Further information about the detector design can be found in \cite{script}.
